### 2021-06-18 README.Rmd
updated readme

#create 2-D samples with the different underlying distributions
sample1Data <- data.frame(
  x = rnorm(n = 100, mean = 0, sd = 3),
  y = rnorm(n = 100, mean = 0, sd = 1)
)
sample2Data <- data.frame(
  x = rnorm(n = 100, mean = 0, sd = 1),
  y = rnorm(n = 100, mean = 0, sd = 3)
)

@@

#create 2-D samples with the same underlying distributions
sample1Data <- data.frame(
  x = rnorm(n = 100, mean = 0, sd = 1),
  y = rnorm(n = 100, mean = 0, sd = 1)
)
sample2Data <- data.frame(
  x = rnorm(n = 100, mean = 0, sd = 1),
  y = rnorm(n = 100, mean = 0, sd = 1)
)

>>>>

#create 2-D samples with the different underlying distributions
sample1Data <- data.frame(
  x = rnorm(n = 50, mean = 0, sd = 3),
  y = rnorm(n = 50, mean = 0, sd = 1)
)
sample2Data <- data.frame(
  x = rnorm(n = 50, mean = 0, sd = 1),
  y = rnorm(n = 50, mean = 0, sd = 3)
)

@@

#create 2-D samples with the same underlying distributions
sample1Data <- data.frame(
  x = rnorm(n = 50, mean = 0, sd = 1),
  y = rnorm(n = 50, mean = 0, sd = 1)
)
sample2Data <- data.frame(
  x = rnorm(n = 50, mean = 0, sd = 1),
  y = rnorm(n = 50, mean = 0, sd = 1)
)
